\begin{recipe}
[
    preparationtime = {\unit[1.5]{h}},
    source = Kamil Krukowski,
    portion = \portion{8}
]
{(Chicken) Tikka Masala Pizza}

\setRecipeColors{
recipename = orange,
numeration = black
}

    \introduction{
    A college student favorite invented in a hazy dream of final exam week. The trick behind this recipe is a sharp pungent cheese and sweet red onion balancing out a spicy and rich chicken tikka masala curry.
    }
    
    \ingredients
    {
            \unit[3.5]{cups} & Chicken Tikka Masala \\
            \\
            \textbf{Dough} & \\
            \\
            4 cups & flour\\
            3 tbsp & oil\\
            1 tbsp & sugar\\
            Some & warm water\\
            1.5 tsp & yeast\\
            \\ 
            \textbf{Topping} & \\
            \\
            2 cups & Pecorino Romano\\
            3 & jalapeno peppers, finely minced\\
            1 medium & red onion, finely diced\\
    }
    
    \preparation
    { 
        \step Bloom yeast by combining slightly warm water with yeast and sugar, let rest for 10 minutes until foamy.
        \step Combine flour, oil, and bloomed yeast. Add half the water and gently mix until barely incorporated. Let rest for 20 minutes to hydrate. Knead dough until uniform, adding flour until it no longer sticks.
        \step Spread out the dough onto a flat greased baking sheet, extra thinly. Bake at 375f for 25-35 minutes or until browned, then flip and remove from the oven.
        \step In a pan, sautee onions and jalapenos until translucent. Separately, reduce Chicken Tikka Masala on high heat until thickened.
        \step Spread chicken tikka masala over the crisped pizza base, top with shredded cheese. Sprinkle with onions and jalapenos, then broil in the oven until the cheese melts.

    }
    
    \hint{
        For extra flavour, brush flattened dough in pan with roasted garlic oil before baking.
    }
    


\end{recipe}
