\begin{recipe}
[
    preparationtime = {\unit[45]{m}},
    source = Kamil Krukowski,
    portion = \portion{8}
]
{Tiramisu}

\setRecipeColors{
recipename = orange,
numeration = black
}
    \ingredients
    {   
            \unit[1]{lb} & lady fingers (About 40) \\
            \unit[\nicefrac{1}{4}]{cup} & cacao powder \\
            \\
            \textbf{Zabaglione} & \\
            4 & egg yolks \\
            \unit[\nicefrac{1}{4}]{cup} & white sugar\\
            \unit[2]{oz} & dark rum \\
            \\
            \textbf{Creme} & \\
            \unit[1]{lb} & mascarpone \\
            \unit[2]{oz} & dark rum \\
            \unit[2]{cups} & heavy cream \\
            \unit[\nicefrac{1}{2}] tsp & vanilla extract\\
            \unit[\nicefrac{1}{8}] tsp & salt\\
            \\
            \textbf{Coffee Syrup} & \\
            \unit[1.5]{cups} & fresh espresso \\
            \unit[2]{oz} & coffee liquor \\
            \unit[\nicefrac{1}{4}]{cup} & white sugar
    }
    
    \preparation
    { 
        \step For the Zabaglione, combine egg yolks with sugar. Whisk vigorously until doubled in volume and pale. Combine with rum in a double broiler setup, whisking to make sure the eggs don't curdle. Once the mixture thickens, take it off the heat.
        \step For the coffee syrup, combine hot espresso with sugar and liquor. Stir to dissolve.
        \step Using a stand mixer, start the Creme by combining mascarpone with vanilla, salt, and rum. Set aside. Prepare whipped cream by beating heavy cream into stiff peaks. 
        \step Slowly fold in the Mascarpone mixture and Zabaglione with the whipped cream, taking care to not deflate the whipped cream.
        \step Assemble by briefly soaking lady fingers in the Coffee Syrup, then arranging them in a layer in a 9x13 pan. Spread half of the Creme-Zabaglione mixture into an even layer.
        \step Repeat with another layer of soaked lady fingers and Creme-Zabaglione. Dust thoroughly with cacao powder, and let refrigerate at least 4 hours.
    }

    \hint{
        \begin{itemize}
            \item Consider substituting the dark rum and/or coffee liquor entirely with Kahlua.
            \item The coffee liquor could be swapped for 3 oz triple sec, i.e. Grand Mariner.
        \end{itemize}
    }

\end{recipe}
